Supporting information: Tail associations and their impact on extinction risk

### 2019-10-30 MainText.Rmd
working on results edits

---
title: "Tail associations and their impact on extinction risk"
author: "Shyamolina Ghosh, Daniel Reuman"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=1in,right=1in,top=1in,bottom=1in"
output: 
  pdf_document:
    number_sections: no
    keep_tex: yes
    fig_caption: yes
    includes:
      in_header: head_maintext.sty

@@

@@

<!--Q2 : metapopulation results : density dependence with extreme tail dep. copula-->

We found density-dependent metapopulation models in stochastic 
environment showed similar patterns for extinction risk as density-independent 
metapopulation model did in a recent study [@Ghosh_copula]. For each density-dependent 
model listed in Table \ref{tab_model_summary}, we observed higher extinction risk for 
the metapopulations when spatially correlated noises were left-tail associated 
than the one with the right-tail association. But that observation remained 
valid when the model parameter - here considered as growth rate $(r)$ - was 
sufficiently low so that under-compensatory dynamics (monotonous approach towards
its stable equilibrium) for the deterministic analog of the model was ensured.
We observed right tail associated noise caused higher extinction 
risk for the metapopulations than left tail associated noise when the model 
was in over-compensatory regime (oscillatory approach towards stable equilibrium) for higher 
value of $r$. Fig. \ref{fig_extrisk_allmodel_localdisp} shows
variation of extinction risk against local dispersal rate ($d$) for 
six density dependent metapopulation models (see Table \ref{tab_model_summary}) with growth 
rate $r$ considered either from under-compensatory or 
from over-compensatory regime. This finding addresses (Q2) from \nameref{Introduction}. We 
also got similar results 
for global dispersal (Fig. \ref{SM-fig_extrisk_allmodel_globaldisp}). 
Figs. (\ref{SM-fig_ricker_risk_local_disp_scl_1} - 
\ref{SM-fig_risk_local_disp_abrewer_r_vary_scl_0.6}) 
demonstrate how extinction risk changed against local dispersal rate for a whole range
of $r$, whereas Figs. (\ref{SM-fig_ricker_risk_global_disp_scl_1} - 
\ref{SM-fig_risk_global_disp_abrewer_r_vary_scl_0.6}) 
represent the same but for global dispersal among patches. 
Both case showed the signature of "rescue-effect" (i.e. reduced the extinction risk for 
finite dispersal compared with $d=0$).

@@

<!--FIG :  summary : all nonlinear model results for local dispersion : extrisk vs. d-->
\begin{figure*}[!h]
\begin{center}
\includegraphics[width=14.5 cm]{./Results/allmodel_ext_risk_local_disp_extreme_and_moderate_noise.pdf}
\caption{Extinction risks are computed after $25$ years for six nonlinear density-dependence models (Table \ref{tab_model_summary}) with local dispersal among $n=5$ patches and for $10000$ simulations. Spatially correlated 
noises have varying degree of tail associations (extreme left tail, moderate left tail, moderate right tail and extreme right tail) as introduced in Fig. \ref{fig_intro_cop}. Last two columns represent variation of extinction risk against dispersal rate ($d$), calculated for intrinsic growth rate $(r)$ taken from under-compensatory and over-compensatory regime of deterministic model analog.\label{fig_extrisk_allmodel_localdisp}}
\end{center}
\end{figure*}

>>>>

---
title: "Tail associations and their impact on extinction risk"
author: "Shyamolina Ghosh, Daniel Reuman"
date: ""
geometry: "left=1in,right=1in,top=1in,bottom=1in"
output: 
  pdf_document:
    number_sections: no
    keep_tex: yes
    fig_caption: yes
    includes:
      in_header: head_maintext.sty

@@

\noindent \emph{Correspondence:} Daniel Reuman, 2101 Constant Ave, Lawrence, KS, 66047, reuman@ku.edu, 626 560 7084.

@@

<!--Q2 : metapopulation results-->
For our metapopulation simulations, for low values of $r$, left-tail
associations of environmental noises accentuated extinction risks, and right-tail associations
mitigated them; but the reverse was true for high values of $r$ in the range
$(r_{min},r_{bf})$. Thus 
density dependent models can either produce similar results, regarding the influence of 
tail associations on extinction risk, as the density-independent models of @Ghosh_copula, or
opposite results, depending on the nature of density dependence. 
For each model of Table \ref{tab_model_summary}, using a value of $r$ on
the low end of the range $(r_{min},r_{bf})$, extinction risk was highest
for extreme left-tail associated noise, lowest for extreme right-tail associated
noise, and was intermediate for the moderate tail association scenarios, for
both local (Fig. \ref{fig_extrisk_allmodel_localdisp}, left panels) and global 
(Fig. \ref{SM-fig_extrisk_allmodel_globaldisp}, left panels) dispersal, and for 
essentially all the dispersal rates, $d$, that we considered. However, 
using a value of $r$ on the high end of the range $(r_{min},r_{bf})$,
extinction risks were ordered oppositely (right panels of Figs 
\ref{fig_extrisk_allmodel_localdisp} and \ref{SM-fig_extrisk_allmodel_globaldisp}). 
These results help address Q2 from the \nameref{Introduction}.
Intermediate values of $r$ are shown in Figs. \ref{SM-fig_ricker_risk_local_disp_scl_1} - 
\ref{SM-fig_risk_local_disp_abrewer_r_vary_scl_0.6} for local dispersal and 
Figs. \ref{SM-fig_ricker_risk_global_disp_scl_1} - 
\ref{SM-fig_risk_global_disp_abrewer_r_vary_scl_0.6} for global dispersal among 
habitat patches.

Because the deterministic, one-patch versions of our models showed undercompensatory
dynamics for $r<r_c$ (and therefore for $r$ on the left end of the range $(r_{min},r_{bf})$),
and showed overcompensatory dynamics for $r>r_c$, Figs \ref{fig_extrisk_allmodel_localdisp}
and \ref{SM-fig_extrisk_allmodel_globaldisp} suggest the hypothesis that the
opposite effects of tail association on extinction risk correspond to the domains
in which models exhibit under- versus overcompensatory dynamics. This was 
approximately, but not exactly, true. Careful inspection of Figs 
\ref{SM-fig_ricker_risk_local_disp_scl_1} - \ref{SM-fig_risk_global_disp_abrewer_r_vary_scl_0.6}
and Table

@@

<!--FIG :  summary : all nonlinear model results for local dispersion : extrisk vs. d-->
\begin{figure*}[!h]
\begin{center}
\includegraphics[width=14.5 cm]{./Results/allmodel_ext_risk_local_disp_extreme_and_moderate_noise.pdf}
\caption{Extinction risk versus dispersal rate for different scenarios of tail association
for our six metapopulation models (Methods, Table \ref{tab_model_summary}). Dispersal was
local, see Fig. \ref{SM-fig_extrisk_allmodel_globaldisp} for global dispersal. Values of $r$
used are in the panel headers.
Extinction risks are for a 25-year time horizon. \label{fig_extrisk_allmodel_localdisp}}
\end{center}
\end{figure*}

### 2019-10-30 SuppMat.Rmd
working on results edits

---
title: "Supporting information: Tail associations and their impact on extinction risk"
author: "Shyamolina Ghosh, Daniel Reuman"
date: "`r format(Sys.time(), '%d %B, %Y')`"
geometry: "left=1in,right=1in,top=1in,bottom=1in"

@@

<!--FIG:  summary: all nonlinear model results for global dispersion: extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_global_disp_extreme_and_moderate_noise.pdf}
\caption[Extinction risk vs. dispersal rate for six density dependent metapopulation model with global dispersal.]{Analogous figure as of Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text but for global dispersal between metapopulation patches.\label{fig_extrisk_allmodel_globaldisp}}
\end{center}
\end{figure}

<!--FIG: Ricker model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Effect of tail association in environmental noises on extinction risk for Ricker metapopulation model with local dispersal.]{Effect of tail association in environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Ricker dynamics with local dispersal; 
standard deviation $\sigma$=1 was used to generate extreme extreme tail dependent noises for 10000 simulations. \label{fig_ricker_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--FIG : Hassell model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Effect of tail association in environmental noises on extinction risk for Hassell metapopulation model with local dispersal.]{Effect of tail association in environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Hassell dynamics with local dispersal; 
standard deviation $\sigma$=1 was used to generate extreme tail dependent noises for 10000 simulations. \label{fig_hassell_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--FIG: Maynard smith model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Effect of tail association in environmental noises on extinction risk for Maynard smith metapopulation model with local dispersal.]{Effect of tail association in environmental noises on extinction risk (calculated after 25 years) for $5$ metapopulation patches which followed Maynard Smith dynamics with local dispersal; 
standard deviation $\sigma$=0.8 was used to generate extreme tail dependent noises for 10000 simulations. \label{fig_msmith_risk_local_disp_scl_0.8}}
\end{center}
\end{figure}

<!--FIG: Pennycuick model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Effect of tail association in environmental noises on extinction risk for Pennycuick metapopulation model with local dispersal.]{Effect of tail association in environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Pennycuick dynamics with local dispersal; 
standard deviation $\sigma$=1 was used to generate extreme tail dependent noises for 10000 simulations. \label{fig_risk_local_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--FIG: Verhulst model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Effect of tail association in environmental noises on extinction risk for Verhulst metapopulation model with local dispersal.]{Effect of tail association in environmental noises on extinction risk (calculated after 25 years)
for $5$ metapopulation patches which followed Verhulst dynamics with local dispersal; 
standard deviation $\sigma$=0.6 was used to generate extreme tail dependent noises for 10000 simulations. \label{fig_risk_local_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--FIG: Austin-Brewer model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Effect of tail association in environmental noises on extinction risk for Austin-Brewer metapopulation model with local dispersal.]{Effect of tail association in environmental noises on extinction risk (calculated after 25 years) for $5$ metapopulation patches which followed Austin-Brewer dynamics with local dispersal; 
standard deviation $\sigma$=0.6 was used to generate extreme tail dependent noises for 10000 simulations. \label{fig_risk_local_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--FIG : Ricker model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_global_disp_extreme_and_moderate_noise.pdf}\\
\caption[Analogous figure as of Fig. \ref{fig_ricker_risk_local_disp_scl_1} but for global dispersal between metapopulation patches.]{Analogous figure as of Fig. \ref{fig_ricker_risk_local_disp_scl_1} but for global dispersal between metapopulation patches. \label{fig_ricker_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--FIG: Hassell model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/hassell_scl_1/hassell_ext_risk_global_disp_extreme_and_moderate_noise.pdf}\\
\caption[Analogous figure as of Fig. \ref{fig_hassell_risk_local_disp_scl_1} but for global dispersal between metapopulation patches.]{Analogous figure as of Fig. \ref{fig_hassell_risk_local_disp_scl_1} but for global dispersal between metapopulation patches. \label{fig_hassell_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--FIG: Maynard smith model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_global_disp_extreme_and_moderate_noise.pdf}\\
\caption[Analogous figure as of Fig. \ref{fig_msmith_risk_local_disp_scl_0.8} but for global dispersal between metapopulation patches.]{Analogous figure as of Fig. \ref{fig_msmith_risk_local_disp_scl_0.8} but for global dispersal between metapopulation patches. \label{fig_msmith_risk_global_disp_scl_0.8}}
\end{center}
\end{figure}

<!--FIG: Pennycuick model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_global_disp_extreme_and_moderate_noise.pdf}\\
\caption[Analogous figure as of Fig. \ref{fig_risk_local_disp_pennycuick_r_vary_scl_1} but for global dispersal between metapopulation patches.]{Analogous figure as of Fig. \ref{fig_risk_local_disp_pennycuick_r_vary_scl_1} but for global dispersal between metapopulation patches. \label{fig_risk_global_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--FIG: Verhulst model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_global_disp_extreme_and_moderate_noise.pdf}\\
\caption[Analogous figure as of Fig. \ref{fig_risk_local_disp_verhulst_r_vary_scl_0.6} but for global dispersal between metapopulation patches.]{Analogous figure as of Fig. \ref{fig_risk_local_disp_verhulst_r_vary_scl_0.6} but for global dispersal between metapopulation patches. \label{fig_risk_global_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--FIG: Austin brewer model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_global_disp_extreme_and_moderate_noise.pdf}\\
\caption[Analogous figure as of Fig. \ref{fig_risk_local_disp_abrewer_r_vary_scl_0.6} but for global dispersal between metapopulation patches.]{Analogous figure as of Fig. \ref{fig_risk_local_disp_abrewer_r_vary_scl_0.6} but for global dispersal between metapopulation patches. \label{fig_risk_global_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}

>>>>

---
title: "Supporting information: Tail associations and their impact on extinction risk"
author: "Shyamolina Ghosh, Daniel Reuman"
date: ""
geometry: "left=1in,right=1in,top=1in,bottom=1in"

@@

<!--FIG:  summary: all nonlinear model results for global dispersion: extrisk vs. d-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=15 cm]{./Results/allmodel_ext_risk_global_disp_extreme_and_moderate_noise.pdf}
\caption[Extinction risk v. tail association and $d$: metapopulations, global dispersal]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but using global dispersal between habitat patches.\label{fig_extrisk_allmodel_globaldisp}}
\end{center}
\end{figure}

<!--FIG: Ricker model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Ricker]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Ricker model.\label{fig_ricker_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--FIG : Hassell model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/hassell_scl_1/hassell_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Hassell]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Hassell model. \label{fig_hassell_risk_local_disp_scl_1}}
\end{center}
\end{figure}

<!--FIG: Maynard smith model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Maynard Smith]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Maynard Smith model. \label{fig_msmith_risk_local_disp_scl_0.8}}
\end{center}
\end{figure}

<!--FIG: Pennycuick model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Pennycuick]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Pennycuick model. \label{fig_risk_local_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--FIG: Verhulst model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Velhurst]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Velhurst model. \label{fig_risk_local_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--FIG: Austin-Brewer model, local dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_local_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, local dispersal, Austin-Brewer]{Analogous to Fig. \ref{MT-fig_extrisk_allmodel_localdisp} in the main text, but considering more values of $r$ and only the Austin-Brewer model. \label{fig_risk_local_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--FIG : Ricker model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=12 cm]{./Results/ricker_scl_1/ricker_ext_risk_global_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, global dispersal, Ricker]{Analogous to Fig. \ref{fig_ricker_risk_local_disp_scl_1} but for global dispersal between habitat patches. \label{fig_ricker_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--FIG: Hassell model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/hassell_scl_1/hassell_ext_risk_global_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, global dispersal, Hassell]{Analogous to Fig. \ref{fig_hassell_risk_local_disp_scl_1} but for global dispersal between habitat patches. \label{fig_hassell_risk_global_disp_scl_1}}
\end{center}
\end{figure}

<!--FIG: Maynard smith model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/msmith_scl_0.8/msmith_ext_risk_global_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, global dispersal, Maynard Smith]{Analogous to Fig. \ref{fig_msmith_risk_local_disp_scl_0.8} but for global dispersal between habitat patches. \label{fig_msmith_risk_global_disp_scl_0.8}}
\end{center}
\end{figure}

<!--FIG: Pennycuick model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/pennycuick_scl_1/pennycuick_ext_risk_global_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, global dispersal, Pennycuick]{Analogous to Fig. \ref{fig_risk_local_disp_pennycuick_r_vary_scl_1} but for global dispersal between habitat patches. \label{fig_risk_global_disp_pennycuick_r_vary_scl_1}}
\end{center}
\end{figure}

<!--FIG: Verhulst model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/verhulst_scl_0.6/verhulst_ext_risk_global_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, global dispersal, Velhurst]{Analogous to Fig. \ref{fig_risk_local_disp_verhulst_r_vary_scl_0.6} but for global dispersal between habitat patches. \label{fig_risk_global_disp_verhulst_r_vary_scl_0.6}}
\end{center}
\end{figure}

<!--FIG: Austin brewer model, global dispersal-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=12 cm]{./Results/common_legend_extreme_and_moderate_noise.pdf}\\
\includegraphics[width=15 cm]{./Results/austinbrewer_scl_0.6/abrewer_ext_risk_global_disp_extreme_and_moderate_noise.pdf}\\
\caption[Extinction risk v. tail association, $d$ and $r$: metapopulations, global dispersal, Austin-Brewer]{Analogous to Fig. \ref{fig_risk_local_disp_abrewer_r_vary_scl_0.6} but for global dispersal between habitat patches. \label{fig_risk_global_disp_abrewer_r_vary_scl_0.6}}
\end{center}
\end{figure}
